Many claims of group polarization are plausibly false due to inappropriate statistics

### 2024-10-29 GroupPolarizationStatmod/paper.bk/ms.tex
updates and started FDR module

We begin by developing a formal model of ordinal measurement of latent continuous
opinions (model variables and parameters are given in Table~\ref{tab:modelVariables}).
First, we assume that participant $i$ has latent opinion at time $t$ that is drawn from
a group-level normal distribution,
\begin{equation}
  o_{i,t} \sim p(o; \mu_t, \sigma_t) = \mathcal{N}(\mu_t, \sigma_t).
  \label{eq:opinionDistribution}
\end{equation}
\noindent 
This distribution has mean $\mu_t$ and standard deviation $\sigma_t$.
This form is chosen to
reflect the common statistical analysis used by group polarization studies,
not because it is statistically appropriate---in fact it is not, which is what
we aim to show in this paper.

>>>>

We begin by developing a formal model of ordinal measurement of latent continuous
opinions (model variables and parameters are given in Table~\ref{tab:modelVariables}).
First, we assume that participant $i$ has latent opinion at time $t$ that is drawn from
a group-level normal distribution,
\begin{equation}
  o_{i,t} \sim p(o; \mu_t, \sigma_t) = \mathcal{N}(\mu_t, \sigma_t).
  \label{eq:opinionDistribution}
\end{equation}
\noindent 
This distribution has mean $\mu_t$ and standard deviation $\sigma_t$.
\mt{The following here goes in intro to justify model choices:} This form is chosen to
reflect the common statistical analysis used by group polarization studies,
not because it is statistically appropriate---in fact it is not, which is what
we aim to show in this paper.
